MSB104_assignment1

### 2023-10-06 MSB104_assignment1.qmd
Descriptive data update 06.10.23

# **Data Acquisition**

## Population per sub-region in DE, FI & RO

@@

## Overview of presented datasets and structure

@@

# **GDP per Capita Calculation**

@@

## Calculation steps

@@

@@

## Litterature review

@@

# GINI

@@

>>>>

# Sub-national GDP and GDP per Capita

## **Data Acquisition**

### Population per sub-region in DE, FI & RO

@@

### Overview of presented datasets and structure

@@

## **GDP per Capita Calculation**

@@

### Calculation steps

@@

## Descriptive Analysis:

```{r}
GDP_DE_nuts2 <- merged_data %>%
  filter(
    str_sub(Sub_regions, start = 1L, end = 2L) == "DE"
  ) |> 
  mutate(
    id_nuts2 = str_sub(Sub_regions, start = 1L, end = 4L)
  ) |> 
  group_by(id_nuts2, Year) %>%
  summarise(
    GDP_per_capita_nuts2_DE = sum(1000000*GDP)/sum(Population)
    ) 
```

```{r}
#| cap-location: bottom
#| fig-cap: "De GNP per år."
GDP_DE_nuts2 |>
  filter(
    as.integer(str_sub(id_nuts2, start = 3L, end = 4L)) >= 0
    )  |>
  filter(
  as.integer(str_sub(id_nuts2, start = 3L, end = 4L)) < 50
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

```{r}
desc_stat_DE_nuts2 <- GDP_DE_nuts2 |> 
  group_by(Year) |> 
  summarise(
    min_GDP_each_year = min(GDP_per_capita_nuts2_DE),
    max_GDP_each_year = max(GDP_per_capita_nuts2_DE),
    median_GDP_each_year = median(GDP_per_capita_nuts2_DE),
    mean_GDP_each_year = mean(GDP_per_capita_nuts2_DE),
    sd_GDP_each_year = sd(GDP_per_capita_nuts2_DE),
    var_GDP_each_year = sd_GDP_each_year^2
  )
```

```{r}
GDP_DE_nuts2 |> 
  ungroup() |> 
  select(Year, GDP_pc = GDP_per_capita_nuts2_DE) |> 
  st(group = "Year", group.long = TRUE, 
     summ = c('notNA(x)','mean(x)', 'median(x)', 
              'sd(x)','min(x)','max(x)'),

     )
```

```{r}
GDP_DE_nuts2 |> 
  filter(Year == 2005) |> 
  select(-Year) |> 
  st()
```

@@

## Literature review

@@

## GINI Coefficient Calculation

@@

## Data presentation

## Discussion

```{r}
#| echo: false
# siste
```
